---
title: "SICSS Project"
author: Ela Castellanos-Reyes
date: '06-16-22'
output: html_notebook
---

# Prepare Workspace

The project is already in my preferred working directory. Regarding loading package pdftools: #When prompted if want to install from sources the packages whihc need compilation say NO. Explanation here <https://community.rstudio.com/t/meaning-of-common-message-when-install-a-package-there-are-binary-versions-available-but-the-source-versions-are-later/2431>

```{r}
pacman::p_load(
  tidyverse,
  pdftools, 
  tesseract
)

setwd("/Users/Ela 1/Documents/LDT Mac/7. ProfessionalDevelopment/SICSS_Project/SICSS-Project-African-Youth-Leadership/Webscraped data")
#install.packages("pdftools")
#setwd(/Users/Ela 1/Documents/LDT Mac/7. ProfessionalDevelopment/SICSS_Project/)
```

Websites used: 
1. <https://www.r-bloggers.com/2018/01/how-to-extract-data-from-a-pdf-file-with-r/> 
2. <https://alexluscombe.ca/blog/getting-your-.pdfs-into-r/> 
3. <https://www.i3s.unice.fr/~malapert/R/pdf/base-r.pdf>

Create an object that has the path of my folder with pdfs

```{r}
dest <- "/Users/Ela 1/Documents/LDT Mac/7. ProfessionalDevelopment/SICSS_Project/SICSS-Project-African-Youth-Leadership/Webscraped data"
```

Create a vector that has the name of the PDF file names. The argument full.names is necessary to obtain the full path.

```{r}
myfiles <- list.files(path = dest, pattern = "pdf", full.names = TRUE)
```

There was a corrupt file!!! "AYLS038_ColumbaLeadership.pdf". After deleting the file things worked well.

```{r}
corpus_raw <- data.frame("org" = c(),"text" = c())
```

Successful loop. Previous versions are in "ElaSandbox.R"

```{r}
for (i in 1:length(myfiles)){
  rawtext <- pdf_text(myfiles[i], opw = "", upw = "") 
  document <- data.frame( #Creates new data frame
                        "org" = gsub(x =myfiles[i],pattern = ".pdf", replacement = ""), #This uses the gsub function of the regular expressions in R
                         "text" = x, stringsAsFactors = FALSE
                        )
  colnames(document) <- c("org", "text")
  corpus_raw <- rbind(corpus_raw,document)
}
```


```{r}

```


